---
title: "kolada-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{kolada-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, eval=TRUE}
library(KoladaPackage)
```

This is a package to retrieve data from the Kolada API. It constructs the API URL based on the function parameter by pasting it together with a pre-defined base URL. The package has a function that finally returns a data frame after parsing data from JSON.

#Example:  
    The way to use the **KoladaPackage** is as follows:
    
    ```{r, include = TRUE, eval = TRUE, echo = TRUE}
    
    result <- get_kolda_data('kpi/n60026/year/2020,2019,2018')
    
    ```
    
  After calling the function as shown above, it returns the following:
    
    ```{r, include = TRUE, eval = TRUE, echo = FALSE}
    
    head(result$MunMaster,5)
    head(result$FinalData,5)
    
    ```
    
  This returns a data frame of required API data that contains a list where first element is master data of names for Municipalities and the second element is a data frame consisting of municipalities' data for the specified KPI and years in the URL.